Best Practices for Single Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-03-12 paper/manuscript.tex
Add final edit  On branch main
 Changes to be committed:
	modified:   manuscript.tex

Concerning SC approaches, Pearlman’s usage of the term single topology not only meant a chimeric construct as depicted in Fig.~\ref{fig:fig_topology}, but specifically implied that the coupling parameter $\lambda$ was applied to the force field parameters. E.g., a bond stretching energy term changing from C-H to C-C has the functional form $U_{bond}(\lambda)=K(\lambda)(r-r_0(\lambda))^2$. For $\lambda=0$, $K(\lambda)$ and $r_0(\lambda)$ correspond to the values appropriate for an aliphatic C-H bond, and for $\lambda=1$ to those for an aliphatic C-C bond. The other energy terms are treated analogously. The single topology paradigm as just summarized was the default mode of alchemical transformations in AMBER and GROMOS at that time.  More recently, this implementation of single topology has been referred to as parameter interpolation or mixing \cite{Giese_2018}.

>>>>

Concerning SC approaches, Pearlman’s usage of the term single topology not only meant a chimeric construct as depicted in Fig.~\ref{fig:fig_topology}, but specifically implied that the coupling parameter $\lambda$ was applied to the force field parameters. E.g., a bond stretching energy term changing from C-H to C-C has the functional form $U_{bond}(\lambda)=K(\lambda)(r-r_0(\lambda))^2$. For $\lambda=0$, $K(\lambda)$ and $r_0(\lambda)$ correspond to the values appropriate for a C-H bond, and for $\lambda=1$ to those for a C-C bond. The other energy terms are treated analogously. The single topology paradigm as just summarized was the default mode of alchemical transformations in AMBER and GROMOS at that time.  More recently, this implementation of single topology has been referred to as parameter interpolation or mixing \cite{Giese_2018}.
